---
title: "q4"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Market Segmentation

The goal of this report is to help NutrientH2O find market segments that may be of interest. For the purposes of this goal, k-means clustering has been used and several different predictors have been plotted to try and understand the market segments present with NutrientH2O's online audience.

```{r loadingdata, echo = FALSE, message=FALSE}
rm(list = ls())
library(ggplot2)
library(LICORS)
library(foreach)
library(mosaic)
library(foreach)
set.seed(52)
social = read.csv('social_marketing.csv', header=TRUE)
rownames(social) <- social$X
social = social[,-1]
```

## Cleaning data
It is important to note that the dataset received from Amazon's Mechanical Turk Service has to be cleaned in order to better understand the market. In order to do this any row which had adult or spam content was deleted from the dataset. The next step taken was to filter out rows with high density of uncategorized and chatter content. Upon closer inspection, it was recognized that several rows had high counts in the chatter column. So, it was decided that any row that had a chatter count of more than 2 would be deleted from the dataset along with rows that had content in the uncategorized column.

```{r cleaning, echo =FALSE, message = FALSE}
social = social[!(social$chatter>=2 | social$adult>=1 | social$spam>=1 | social$uncategorized>=1),]
```

## Scaling data
After cleaning the dataset, steps were taken to scale the dataset.In the process of scaling, columns for adult, spam, uncategorized and chatter were deleted. The means and the standard deviations of the dataset were saved so that they could be reverted back to understandable data points once clusters were made.

```{r scaling, echo = FALSE, message = FALSE}
X = social
X = X[,-5]
X = X[,-(34:35)]
X = X[,-1]
X_for_elbow = X
X = scale(X, center=TRUE, scale=TRUE)
mu = attr(X,"scaled:center")
sigma = attr(X,"scaled:scale")

```

## Choosing a value for k
In order to create the model, a number had to be chosen for the k. The Gap statistic method was first used for this purpose. The plot from the gap statistic method is shown:

```{r gap, echo = FALSE,fig.align='center', fig.height = 5, fig.width = 8,echo = FALSE, message = FALSE, warning = FALSE}
library(cluster)
mark_gap = clusGap(social, FUN = kmeans, nstart = 50, K.max = 20, B = 100)
plot(mark_gap)

```

As can be seen, no clear dip could be observed. So, it was decided after several trials that a k value of 7 would be chosen. This was based on formation of discernible clusters for this specific value of k.

## Identifying clusters
At first, a combination of different variables were plotted. One of the first pairs of covariates that showed an interesting cluster was beauty and fashion.

```{r beatyfasion, echo = FALSE,fig.align='center', fig.height = 5, fig.width = 8}
clust1 = kmeanspp(X, 7, nstart=25)
qplot(fashion, beauty, data=social, color=factor(clust1$cluster))

```

The concentration of members of the same cluster for higher number of tweets in fashion and beauty suggests that it is a pretty clear cluster which can considered as an exploitable market.This cluster can be thought as consisting of young individuals who are interested in appearance and fashion trends.

Driven by this finding of clusters formed by individuals who were interested in fashion and beauty, another plot was created with the covariates of travel and personal_fitness.

```{r travelfit, echo = FALSE,fig.align='center', fig.height = 5, fig.width = 8}
qplot(travel, personal_fitness, data=social, color=factor(clust1$cluster))

```

In the plot above, two other clusters emerge: one of people who are very interested in personal fitness and another group for individuals who are very interested in travel. In order to see if the cluster of people interested in personal fitness were in someway also interested in playing sports, another plot was created.

```{r fitsport, echo = FALSE,fig.align='center', fig.height = 5, fig.width = 8}
qplot(sports_playing, personal_fitness, data=social, color=factor(clust1$cluster))

```
The above plot suggests that the hypothesis of the existence of a market segment that is interested in both playing sports and fitness is invalid. However, in order to further investigate if the brand's audience included active college students, a plot was created with the variables college_uni and sports_playing. 

```{r sportuni, echo = FALSE,fig.align='center', fig.height = 5, fig.width = 8}
qplot(college_uni, sports_playing, data=social, color=factor(clust1$cluster))

```
The existence of two distinct clusters is clear in the plot above. One with individuals who attend college and have an active lifestyle and another with neither one of those qualities.Since the demographic that goes to college and plays sports consists of young adults, further investigation was conducted into the online gaming community since its membership is dominated to a certain extent by young adults.

```{r gametrave, echo = FALSE,fig.align='center', fig.height = 5, fig.width = 8}
qplot(travel, online_gaming, data=social, color=factor(clust1$cluster))

```
From the above plot, it is clear that there is cluster of individuals who are heavily involved in online gaming and are interested in NutrientH2O.In an effort to see if there exists clusters among tech savvy individuals, the covariates online_gaming and computers were plotted.

```{r componli, echo = FALSE,fig.align='center', fig.height = 5, fig.width = 8}
qplot(online_gaming, computers, data=social, color=factor(clust1$cluster))

```

This shows that there are actually two distinct clusters: a group for online gamers and others who are solely interested in computers. So this could be interpreted as clusters for younger individuals and another for possibly older individuals just interested in computers.

In an effort to understand if individuals who were interested in healthy eating were a target audience, a plot was made using personal_fitness and health_nutrition. As can be seen below, two distinct clusetrs form: one whose membership consists of individuals interested in healthy eating and personal fitness and another who are not interested in either.


```{r healthfit, echo = FALSE,fig.align='center', fig.height = 5, fig.width = 8}
qplot(health_nutrition, personal_fitness, data=social, color=factor(clust1$cluster))
```


It is worth noting that other covariates such as politics, news, family etc. were plotted but informative clusters were not found. 

## Conclusion

From the above analysis it is clear that the brand NutrientH2O appeals to certain groups of the general populace, namely:

-individuals interested in beauty and fashion: possibly the younger side of the population who follow influencers.
-active individuals attending college: a demographic primarily between the ages of 18 and 22.
-fitness obsessed individuals.
-individuals interested in travel.
-online gamers: once again, most likely a younger portion of the population.
-individuals interested in technology.



